\begin{rubric}{Work experience}
\entry*[Sep 2023 -- Oct 2024]\textbf{Nethone/Mangopay}\newline
    Senior Python Engineer\newline
    Maintaining online payment security software. Ownership of anti-money
        laundering sub-project. Designing the feature based on business needs
        of the stakeholders. Performing dev-ops duties with distributed
        k8s-based architecture.\newline
    \textit{fastAPI, Pyramid, SQLAlchemy}
\entry*[Oct 2019 -- Nov 2023]\textbf{Egnyte}\newline
    Senior Software Engineer\newline
    Maintaining the legacy django-based monolythic monetization app, while working
        on a new microservice-based ecosystem. Cooperation on the main
        spring-based product, enabling the monetization-related features\newline
    \textit{django, fastAPI, ReactJS, Java Spring}
\entry*[Feb 2017 -- Sep 2019]\textbf{Sunscrapers}\newline
    Python engineer in 15Five and Verve projects. Maintaining and expanding
        djang-based web applications.\newline
    \textit{django}
\entry*[Mar 2016 -- Jan 2017]\textbf{Mirantis}\newline
    Software engineer\newline
    Developing components for \textit{kubernetes} environment\newline
    \textit{k8s, go, python}
\entry*[Oct 2013 -- Feb 2016]\textbf{Allegro Group}\newline
    Software engineer\newline
    Creating internal projects for infrastructure. Developing applications for
        asset management and internal DNS configuration tools\newline
    \textit{Django, Pyramid, Bootstrap, PowerDNS}
\entry*[May 2011 -- Sep 2013]\textbf{STX Next}\newline
    Python programmer\newline
    Implementing banking workflows using a dedicated framework based on Pylons
    Development support for deployment of data-management systems for major
    pharmaceutical companies (ousourced to \textit{Steeprock Inc})\newline
    \textit{Pylons, Pyramid, ExtJS}
\entry*[Jun 2009 -- Apr 2011]\textbf{Emtronet/VMR}
    PHP/JS developer\newline
    creating CMS and~\hbox{ecommerce} projects for various clients\newline
    \textit{cakePHP i jQuery}
\entry*[other]Taking part as a speaker in conferences like:\newline
    PythonPL, EuroPython
\end{rubric}
